Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-24 manuscript/manuscript.Rmd
added a TAC sentence

Similarly, we use the following dynamical model in place of eq. \eqref{eq:3d model}
\begin{align*}
  \label{eq:3d model stoch}
  \begin{split}
    \Delta X_t &= L(X_t;\ r_X, K_X) - F(X_t, Z_t;\ \beta, c) - c_{XY}X_tY_t - h_t + \eta_{X,t},\\
    \Delta Y_t &= L(Y_t;\ r_Y, K_Y) - D F(Y_t, Z_t;\ \beta, c) - c_{XY}X_tY_t + \eta_{Y,t},\\
    \Delta Z_t &= \left(f(X_t + DY_t\right) - d_Z)Z_t + \eta_{Z,t}.
\end{split}
\end{align*}
Here, again, $\{\eta_{i,t}\}$ is a set of independent Gaussian variables centered at zero with variances, respectively, $\sigma_X^2$, $\sigma_Y^2$ and $\sigma_Z^2$.

@@

\textbf{Tuning the constant mortality strategy.}
A grid of 200 mortality rates was laid in the interval $[0, 0.1]$.
For each one of these rates, say $F$, we simulated 50 episodes based on \eqref{eq:3d model stoch}:
At each time step the state $(X_t, Y_t, Z_t)$ was observed, a harvest of $FX_t$ was collected and then the system evolved according to its natural dynamics \eqref{eq:3d model stoch}.
The optimal mortality rate was the value $F^*$ for which the mean episode reward was maximal.

\textbf{Parameter values used.}

>>>>

Similarly, we use the following dynamical model in place of eq. \eqref{eq:3d model}
\begin{align}
  \label{eq:3d model stoch}
  \begin{split}
    \Delta X_t &= L(X_t;\ r_X, K_X) - F(X_t, Z_t;\ \beta, c) - c_{XY}X_tY_t - h_t + \eta_{X,t},\\
    \Delta Y_t &= L(Y_t;\ r_Y, K_Y) - D F(Y_t, Z_t;\ \beta, c) - c_{XY}X_tY_t + \eta_{Y,t},\\
    \Delta Z_t &= \left(f(X_t + DY_t\right) - d_Z)Z_t + \eta_{Z,t}.
\end{split}
\end{align}
Here, again, $\{\eta_{i,t}\}$ is a set of independent Gaussian variables centered at zero with variances, respectively, $\sigma_X^2$, $\sigma_Y^2$ and $\sigma_Z^2$.

@@

\textbf{Tuning the constant mortality strategy.}
A grid of 200 mortality rates was laid in the interval $[0, 0.1]$.
For each one of these rates, say $F$, we simulated 50 episodes based on \eqref{eq:3d model stoch}:
At each time step the state $(X_t, Y_t, Z_t)$ was observed, a harvest of $FX_t$ was collected and then the system evolved according to its natural dynamics \eqref{eq:3d model stoch}.
The optimal mortality rate was the value $F^*$ for which the mean episode reward was maximal.
We additionally evaluated a more conservative strategy where a mortality of $0.8 F^*$ instead is used.

\textbf{Parameter values used.}
The model's dynamic parameters were chosen as follows
\begin{align*}
  r_X = K_X = r_Y = K_Y = 1, \quad \beta = 0.3, \quad c = 0.1\\
  c_{XY} = 0.5,\quad f = 0.15,\quad D = 1.1, \quad d_Z = 0.135.
\end{align*}
Moreover, the variances for the stochastic terms were chosen as
$$
  \sigma^2(\eta_{X,t}) = \sigma^2(\eta_{Y,t}) = \sigma^2(\eta_{Z,t}) = 0.05.
$$
The threshold values used to determine an early episode end were chosen as
$$
  X_{\text{thresh.}} = 0.08,\quad Y_{\text{thresh.}} = Z_{\text{thresh.}} = 10^{-4},
$$
where the higher value of $X_{\text{thresh.}}$ helped select for more sustainable fishing strategies (for both the DRL and constant mortality approaches).
